---
title: "Library Prep. Report"
date: "`r Sys.Date()`"
output: html_document
params:
        stan:  NA
        out:   NA
        samp:  NA
        conc:  NA
        slope: NA
---



```{r echo = FALSE, message = FALSE}
library(ggplot2)
library(knitr)
```

:::: {style="display: flex; align-items: center;"}

::: {style="flex-basis: 200px; flex-grow: 2"}
```{r standards_plot, echo = FALSE, warning = FALSE, fig.height=3, out.width="100%"}
params$stan
```
:::


::: {style="flex-basis: 100px; flex-grow: 1"}
Theoretical (perfectly diluted) samples are in gray, true dilutions are in blue. Samples are in red. Dilutions between standards shown in text.
:::

::::


:::: {style="display: flex; align-items: center;"}

::: {style="flex-basis: 200px; flex-grow: 2"}
```{r outliers_plot, echo = FALSE, warning = FALSE, fig.height=5, fig.width = 7.5, out.width="100%"}
params$out
```
:::

::: {style="flex-basis: 100px; flex-grow: 1"}
CT-values as represented by Z-score. Blue dots represent samples not considered outliers. Shaded blue region is +/- three standard deviations, which is considered the cutoff for outliers. Black dots are samples considered outliers. Far outliers (greater than 11 standard deviations) are represented by arrows (>>>) with the true value displayed beside it. Z scores are calculated after removing the outlier, if any. 
:::

::::


:::: {style="display: flex; align-items: center;"}

::: {style="flex-basis: 200px; flex-grow: 2"}
```{r concentration_plot, echo = FALSE, warning = FALSE, out.width="100%"}
params$conc
```
:::

::: {style="flex-basis: 100px; flex-grow: 1"}
Library concentrations across samples
:::

::::

:::: {style="display: flex; align-items: center;"}

::: {style="flex-basis: 200px; flex-grow: 2"}
```{r slope_plot, echo = FALSE, warning = FALSE, message = FALSE, out.width="100%"}
params$slope
```
:::

::: {style="flex-basis: 100px; flex-grow: 1"}
Log of library quantities vs CT values. An optimal slope is -3.32. An optimal efficiency is 100%. Acceptable efficiencies are >80%.
:::

::::

```{r sample_summary, echo = FALSE}
kable(params$samp)
```


